---
title: "Data preparation"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/bib/style.css"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---


```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_prep-data-A.Rmd",output_format = "html_document",output_dir = "production/");browseURL(url = "production/prod_prep-data-A.html")
```

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE,results = "hold")
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

load packages
```{r}
library(sjPlot)
library(sjmisc) # several functions,ej read_stata
library(descr)
library(memisc)  # codebook
library(psych) # cor2latex
library(corrplot) # graph correlations
library(lavaan)
library(stargazer)
library(semTools)
library(plyr) # count
library(dplyr)
#library(car) # recode
library(ggplot2)
#library(Hmisc)
library(tidyverse)
library(data.table)
library(stringr)
library(countrycode)
library(lme4)
library(texreg)
library(mice)
library(ggrepel) # for scatter labels in sjp.scatter
#library(semPlot)
library(haven)
library(sjlabelled)
library(kableExtra)
library(summarytools)



#library(Hmisc)
```


# Open data and General setting

```{r}
issp2009=read_stata("input/data/original/ZA5400_v4-0-0.dta")
   
    # Check data  
    #names(issp2009)
```

```{r}
names(issp2009) <- tolower(names(issp2009)) # change to small
```

## Check & generate IDs (v4: respondent, v5: country)

```{r}
    
# Generate new sequential id individuals by country to merge
      issp2009$id <- sequence(tabulate(issp2009
                                     $v5))
    issp2009$idtem=issp2009$v5*10000  
    issp2009$id=issp2009$idtem + issp2009$id
```



# Measurement Merit & Getting ahead

Note: object now generated from different
script (merit_per_pref.R; merit_per_pref.rda)

##  Measurement and Redistribution

##  Data preparation, gen redistrib.rda    

| Code | New Code   | Variable                                                                                                        |
|------|------------|-----------------------------------------------------------------------------------------------------------------|
| v33  | income_dif | Gov. resp to reduce differences in income                                                                       |
| v34  | unemployed | Gov. resp to provide decent s andard of living for unemployed                                                   |
| v36  | taxes      | People with high income should pay a larger / same smaller share of income in taxes than those with low income |
| v38  | health     | ok if people with high income can buy better health                                                             |
| v39  | educ       | ok if people with high income can buy better education                                                          |                                                         |
###  Rename & define object
 
```{r results='asis'}
# select
    redistrib=issp2009[,c("v5","v33","v34","v36","v38","v39","id")]
   
# new names(issp2009)
    redistrib$income_dif= redistrib$v33
    redistrib$unemployed= redistrib$v34
    redistrib$taxes     = redistrib$v36
    redistrib$health    = redistrib$v38
    redistrib$educ      = redistrib$v39

#Delete old variables
   
    redistrib=redistrib[-c(2:6)]
   
    stargazer(redistrib[-c(1,2)], type="html")  

   
```


### Recode NAs
```{r results='asis'}
    redistrib[3:7][redistrib[3:7] > 5] <- NA
   stargazer(redistrib[-c(1,2)], type="html") 

```


### adjust labels NAs
```{r}
     get_labels(redistrib$income_dif)
    redestrib <-sjlabelled::set_na(redistrib[,c("income_dif","unemployed", "taxes", "health", "educ")], na = c(8,9))  
   
```

### Aggregated data **x**

```{r}

  # Dataset with original code for sjp.likert graph
      redistrib2=redistrib
 
  # Reverse code for SEM models
      redistrib[3:7]=6-redistrib[3:7]
     
  # Checks
redistrib_agg <- aggregate(redistrib, by=list(redistrib$v5), FUN=mean,na.rm=TRUE) 


# En analisis me falta esta base de datos, no estoy seguro de como debe guardarse. 
     
  # Save object
     # save(redistrib, file="input/data/proc/redistrib.rda")
 
```

### General Check "redistrib.rda"
```{r}
print(dfSummary(redistrib_agg, valid.col = FALSE, graph.magnif = 1),
      max.tbl.height = 300, method = "render")
```


```{r}
#############################################
# Ver donde va este codigo. (agregar a prodcution)
###################################################################################################################### 2.5 Invariance
  #   measurementInvariance(cfa_2, data = redistrib.agg, group = "v5")      # No funciono la invarianza arreglar.

```



 End sec 2; saved objects
 # redistrib.rda: clean & recoded
 # redistrib_sco.rda : fac scores   [por ahora en analysis]
 # __propuesta__ redistrib.agg

# Preparation Individual & Macro variables.

## Individual level variables


```{r}
  indepvar=issp2009
#length(indepvar$id)
```

### Recode sex
```{r}
# Sex
sjPlot::plot_frq(indepvar$sex, title ="Before")
indepvar$sex=ifelse(indepvar$sex==1,0,ifelse(indepvar$sex==2,1,NA))  
sjPlot::plot_frq(indepvar$sex, title ="After")
```


### Recode Age
```{r}

label<- c("")
label<- "1"
  # Age
sjPlot::plot_frq(indepvar$age, title = "Before",show.mean = T , show.values = F,show.n = F, axis.labels =)

#which(indepvar$age > 85) # / 461 casos !
#which(indepvar$age < 15) # / 0 casos !
indepvar$age[indepvar$age > 85] = NA

# Categorical age
indepvar$age_c=indepvar$age
indepvar$age_c[indepvar$age_c <= 25] = 1
indepvar$age_c[indepvar$age_c > 25 & indepvar$age_c <=35] = 2
indepvar$age_c[indepvar$age_c > 35 & indepvar$age_c <=45] = 3
indepvar$age_c[indepvar$age_c > 45 & indepvar$age_c <=55] = 4
indepvar$age_c[indepvar$age_c > 55 & indepvar$age_c <=65] = 5
indepvar$age_c[indepvar$age_c > 65] = 6

sjPlot::plot_frq(indepvar$age_c, title = "After", show.na = T)


```


### Recode Education

```{r}
sjPlot::plot_frq(indepvar$degree, coord.flip = TRUE, title = "Before")
```

```{r}
  # Recode. Values over 5 are removed

  indepvar$degree[indepvar$degree > 5]=NA


 
```

#### Dummy university
```{r}
# Dummy university
  indepvar$univ=indepvar$degree
  indepvar$univ=ifelse(indepvar$univ<=4,0,
  ifelse(indepvar$univ==5,1,NA))

  
  sjPlot::plot_frq(indepvar$univ, coord.flip = TRUE, title = "Dummy university")

```




### Recode Income
```{r results='asis'}
  stargazer(indepvar[182:222], type="html")
```


```{r results='asis'}
  # Income (variables finish in _inc)
# Continuo
   
   # Recode missings
      # Para todos los paises, recode missings.  
      indepvar[182:222][indepvar[182:222] >= 9999990] <- NA
      indepvar[182:222][indepvar[182:222] == 999990] =NA
      indepvar[182:222][indepvar[182:222] == 999997] =NA
  indepvar[182:222][indepvar[182:222] == 999998] =NA
  indepvar[182:222][indepvar[182:222] == 999999] =NA
 

    # Identificar ceros (para poder diferenciar de los NAs luego)
    indepvar[182:222][indepvar[182:222] == 0] <- 111111

    
   
  # Agregar ahora todos en un solo vector
indepvar$income=rowSums(indepvar[182:222],na.rm = TRUE)

indepvar$income[indepvar$income ==0]=NA
indepvar$income[indepvar$income ==1111]=0

stargazer(indepvar[182:222], type="html")


```

```{r}
summary(indepvar$income)
```


### Recode Household income

```{r}
# Household income

# Preparar numero de personas en household
indepvar$hompop[indepvar$hompop==99]=NA

# Ahora dividir el vector income por n° de personas en hogar
indepvar$hhincome=indepvar$income/indepvar$hompop
summary(indepvar$hhincome)
 
# Y ajustar NAs de la variable final ingreso continuo
indepvar$hhincome[indepvar$hhincome==0]= NA
indepvar$hhincome[indepvar$income==111111]= 0
indepvar$hhincome[indepvar$hompop==0]= NA

summary(indepvar$hhincome)
```


```{r}
# check
income=indepvar[c("v5", "ar_inc", "hompop","income",
"hhincome")]
# View(income)  

# Generar quintiles de ingreso
indepvar %>% group_by(v5) %>% mutate(quintile =
ntile(hhincome,5)) ->indepvar

# Check
prop.table(table(indepvar$v5,indepvar$quintile),1)*100

```

```{r}
# Generar quintiles con NA como categorÃ?a
indepvar$quintile_miss=indepvar$quintile
indepvar$quintile_miss[is.na(indepvar$quintile_miss)] = 6

summary(indepvar$quintile_miss)
```


### Recode Subjetive status
```{r}

  # Subjective status
   
# Individual
#freq(indepvar$v44)
indepvar$sstatus=indepvar$v44
indepvar$sstatus[indepvar$ssttus>10]=NA
  #freq(indepvar$sstatus)
   
    # Family
#freq(indepvar$v45)
indepvar$f_sstatus=indepvar$v45
    indepvar$f_sstatus[indepvar$f_sstatus>10]=NA
  #freq(indepvar$f_sstatus)


# Home value (ver Nota 3)
summary(indepvar$v67)

```

```{r}
  # Party
    #freq(issp2009$party_lr)
#prop.table(table(indepvar$v5,indepvar$party_lr),1)*100
# paises sin datos: CL, CN, CY, HU, IL, TW
#freq(indepvar$cl_prty) # estan
#freq(indepvar$cn_prty) # no
#freq(indepvar$cy_prty) # si
#freq(indepvar$hu_prty) # si
#freq(indepvar$il_prty) # si
#freq(indepvar$tw_prty) # si

# para usarlas habría que clasificar partidos de esos países

```


## Indep macro var

### Load
```{r}
# Inequality swiid (4)        
swiid = read_stata("input/data/original/swiid8_2.dta")


# convertir desde formato original list a dataframe
#swiid_summary <- swiid %>%  bind_rows() %>%
#group_by(country, year) %>%  
#summarize_all(funs(mean, sd)) %>%
#ungroup() %>% rename(.dots=setNames(names(.),
#str_replace(names(.), "_mean", ""))) %>%  
#rename_(.dots=setNames(names(.),
 #     str_replace(names(.), "_sd", "_se")))

```

###  Filter only 2009
```{r}
#summary(swiid_summary$.dots...year)

#swiid_summary09=subset(swiid_summary, .dots...year==2009)

```


###  Merge with indepvar object
```{r}
# Generate equivalente country code

#head(swiid_summary09$.dots...country)
#as.numeric(swiid_summary09$country)
 
# Continuo
#swiid_summary09$v5=countrycode(swiid_summary09$.dots...country,'country.name','iso3n')
#str(swiid_summary09$v5)

# Categórico
#swiid_summary09$v5c=countrycode(swiid_summary09$.dots...country,'country.name','iso3c')
#str(swiid_summary09$v5c)

# Merge
#indepvar <- merge(swiid_summary09,indepvar,by=c("v5"))
#summary(indepvar$.dots..._1_gini_disp)


```

#### agregate ========
```{r}
# aggregate(indepvar[c("v5","gini_net")],list(indepvar$v5c.x,indepvar$.dots...country),mean) #Buscar como #agregar la variable
```

```{r}

# Quality of government
# los objetos se generan en la sintax qog_explore

# Merge qog
load("input/data/proc/qog_merit.rda")
names(qog_merit)
indepvar <- merge(qog_merit,indepvar,by=c("v5"))
# #freq(indepvar$wdi_gini)

# Generate object
# save(indepvar, file="input/data/proc/indepvar.rda")
#
##
#



```

End sec 3 objeto: indepvar.rda -------

```{r}
load(file = "input/data/proc/indepvar.rda")

print(dfSummary(indepvar, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

#  MODELS B: PREFERENCES  



```{r}

# 5.1 Data preparation
 
  # Load & merge
 
 load("input/data/proc/indepvar.rda")
 
 load("input/data/proc/redistrib.rda")
 load("input/data/proc/redistrib_sco.rda")
length(redistrib$accum)


### aggregate(redistrib[c("redist","accum")],by=list(v5),FUN=mean, na.rm=TRUE)

# Check legths for merge


 # Merge  (to the x, indepvar, largest)
 pref=merge(redistrib_sco, indepvar, by=c("id"), all.x = TRUE)
 #names(pref)

 

# Check
# dim(pref)
#length(pref$v5.x)
#  aggregate(pref[c("v5.x","gini_net","redist")],list(pref$country, pref$v5c),mean, na.rm=TRUE)


#  mean(pref$redist, na.rm=TRUE)
# pref$v5=pref$v5.x
#  
#  summary(pref$redist)
#  summary(pref$id)
 
# Generate level 2 aggregated vars
# names(pref)
# agg_lm=aggregate(pref[c(4:10,22:42)], by=list(pref$v5),FUN=mean, na.rm=TRUE)

# names(agg_lm)
# dim(agg_lm)

# colnames(agg_lm) <- paste("j", colnames(agg_lm), sep = "_")
#  table(agg_lm$v5=agg_lm$j_v5)
 
#  pref2=merge(pref,agg_lm, by="v5")
# pref=pref2
#  dim(pref)

# Group mean centering
  #  pref$age_g=age-j_age
  #  pref$sex_g =sex-j_sex
  #  pref$univ_g =univ-j_univ
  #  pref$sstatus_g= sstatus-j_sstatus
  #  
  #  summary(pref$univ_g)
  #  names(pref)
   
  # Save
  #  save(pref, file = "input/data/proc/pref.rda")
   
```

```{r}
# 6.1 Data preparation - meritocracy.rda  
 
  # Load & merge
#  load("input/data/proc/getahead.rda")
#  load("input/data/proc/indepvar.rda")
#  #names(indepvar)
#  load("input/data/proc/merit_per_pref_sco.rda")
# #names(merit_per_pref_sco)
#
# Check legths for merge
# length(indepvar$id)
# summary(indepvar$id)
#  length(getahead$id)
#  summary(getahead$id)

 # Merge  (to the x, indepvar, largest)
#  meritocracy=merge(merit_per_pref_sco, indepvar, by=c("id"))
#  #names(meritocracy)

# # Check
#  dim(meritocracy)
# length(meritocracy$v5.x)
#  #aggregate(meritocracy[c("v5.x","gini_net","merit")],
 # list(meritocracy$country, meritocracy$v5.x),mean, na.rm=TRUE)
#  mean(meritocracy$merit, na.rm=TRUE)
#  meritocracy$v5=meritocracy$v5.x
 
# Generate level 2 aggregated vars
# names(meritocracy)
#agg_lm=aggregate(meritocracy,by=list(meritocracy$v5c),
# FUN=mean, na.rm=TRUE)
# names(agg_lm)
# dim(agg_lm)

# colnames(agg_lm) <- paste("j", colnames(agg_lm), sep = "_")
#   names(agg_lm)
#  agg_lm$v5=agg_lm$j_v5
#  meritocracy2=merge(meritocracy,agg_lm, by="v5")
#  dim(meritocracy2)
# meritocracy=meritocracy2
#  dim(meritocracy)
 

# Group mean centering
#    meritocracy$age_g=meritocracy$age-meritocracy$j_age
#    meritocracy$sex_g =meritocracy$sex-meritocracy$j_sex
#    meritocracy$univ_g =meritocracy$univ-meritocracy$j_univ
#  meritocracy$sstatus_g= meritocracy$sstatus-meritocracy$j_sstatus
   
#    summary(meritocracy$univ_g)
  #  names(meritocracy)
   
  # Save
 #   save(meritocracy, file = "input/data/proc/meritocracy.rda")
 

```




```{r}
# Adjust data
    pref_agg=aggregate(pref, by=list(pref$v5c),
    	FUN=mean, na.rm=TRUE)
    names(pref_agg)[names(pref_agg)=="Group.1"] <- "v5c"
    	
  # Macro descriptives
    
    
    hist(pref_agg$gini_net)
   table(pref_agg$accum)   
   
    save(pref_agg, file = "input/data/proc/pref_agg.rda")
```






